API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
Emphasize that we consider a dataset a pair of matrix

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, ..., X_p$, called features, and
some output variable $Y$. A sample is then defined as a tuple of values $([x_1,
..., x_p]^\mathrm{T}, y)$ of these variables and a dataset as a collection of
such samples.  As such, matrices of numerical values constitute a natural and
widely used representation in machine learning: each row in the
matrix corresponds to one sample of the dataset and each column to one
variable of the problem.

>>>>

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, ..., X_p$, called features, and
some output variable $Y$. A sample is then defined as a pair of input/output
values $([x_1,..., x_p]^\mathrm{T}, y)$. of these variables. A widely used
representation of a dataset, a collection of
such samples, is a set of two matrix of numerical values: one for the input
values and one for the output values. Each row of these matrix
corresponds to one sample of the dataset and each column to one variable of
the problem.
